Amazon in Presidential Speeches in Brazil (Inductive Analysis)

### 2021-10-18 data_exploration.Rmd
Updated data exploration script by subsetting data

```{r}
BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
BR_Presidential_Speeches <- head(BR_Presidential_Speeches)
BR_Presidential_Speeches$amazon <- poldis::context("Amazon|Amazonica|Amazonia|Amazonas", var = BR_Presidential_Speeches$text
                                                   )

```

>>>>

```{r}
library(dplyr)
BR_Presidential_Speeches <- readRDS("~/GitHub/amazondef/BR_Presidential_Speeches.Rds")
BR_Presidential_Speeches$amazon <- poldis::context("Amazon|Amazonica|Amazonia|Amazonas", var = BR_Presidential_Speeches$text, level = "sentences")
Amazon_speeches <-dplyr::filter(BR_Presidential_Speeches, grepl("Amazon|Amazonica|Amazonia|Amazonas", text))
```
